Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-28 rates-neurips-21/appendix.tex
rates appendix

\begin{lemma*}[Lemma \ref{lemma:polyhedral-finite}]
  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
\end{lemma*}
\begin{proof}
  This follows from results in \cite{finocchiaro2019embedding}.
  \botodo{I'll go ahead and prove this, because it's the main upper bound. TODO}
%  We rely on concepts in \cite{finocchiaro2019embedding}.
%  If $L$ is polyhedral, then define $G: \simplex \to \reals$ to be the negative of its Bayes risk, i.e. $G(p) = -\risk{L}(p) = - \min_{u \in \reals^d} \inprod{p}{L(u)}$.
%  We claim $G$ is a polyhedral function.\bo{why?}
%  \bo{TODO}
\end{proof}

>>>>

\begin{lemma*}[Lemma \ref{lemma:polyhedral-finite}]
  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$. Also, these level sets are polytopes.
\end{lemma*}
\begin{proof}
  This can be deduced from the embedding framework of \cite{finocchiaro2019embedding}.
  Lemma 5 states that if $L$ is polyhedral, then the negative of its Bayes risk, $G(p) = -\risk{L}(p)$, is polyhedral.
  (In other words, the Bayes risk is the concave equivalent of a polyhedral function.)
  Recall that by definition, $\Gamma(p) = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$.
\end{proof}
